Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection\thanks{This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).}

### 2017-01-06 paper/DASFAA17_regular_64.tex
prepare to camera ready

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\titlerunning{Transfer Learning for Accurate Event Detection\ }
\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}

@@

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel category-level transfer learning method \textsc{TransDetector} to deal with the task.  
\textsc{TransDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and events can be detected more accurately on microblogs with richer semantics.
%文本短，建模很困难；直接做迁移学习困难，两者的组织结构不同，如何从精心构造的知识库迁移到微博是一个很大的挑战。
%所以我们提出了Category-Level Transfer Learning ...
The following contributions are made in \textsc{TransDetector}.
(1) We propose a structure-guided category-level topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
(2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
%Hence, word time series are expanded as category-pivot word time series.
(3) Events are detected accurately on category-level word time series, due to richer semantics and less noise. 
(4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
\textsc{TransDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。

\end{abstract}

\section{Introduction}
Many web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
Although event detection has been a research topic for a long while\cite{allan1998topic}, event detection in microblog stream is still challenging\cite{atefeh2015survey}.
According to \cite{huang2016probabilistic}, the characteristics of microblog, which is fast changing, high noise, and short length, raise the challenge.

@@

\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).
%\newpage
\bibliographystyle{unsrt}
\small
\bibliography{paperbib}

>>>>

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection\thanks{This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).}}
\titlerunning{Transfer Learning for Accurate Event Detection\ }
\author{Weijing Huang\inst{1} \and Tengjiao Wang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Yazhou Wang\inst{1} }
\institute{\(^{1}\)Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{tjwang,pekingchenwei}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}

@@

\begin{abstract}
Many Web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods is still challenged by microblog's short length and high noise. 
We develop a novel category-level transfer learning method \textsc{TransDetector} to deal with the task.  
\textsc{TransDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and events can be detected more accurately on microblogs with richer semantics.
%文本短，建模很困难；直接做迁移学习困难，两者的组织结构不同，如何从精心构造的知识库迁移到微博是一个很大的挑战。
%所以我们提出了Category-Level Transfer Learning ...
The following contributions are made in \textsc{TransDetector}.
(1) We propose a structure-guided category-level topics extraction method, which exploits the knowledge base's hierarchical structure to extract categories' highly correlated topics. 
(2) We develop a probabilistic model CTrans-LDA for category-level transfer learning, which utilizes the word co-occurrences and transfers the knowledge base's category-level topics into microblogs. 
%Hence, word time series are expanded as category-pivot word time series.
(3) Events are detected accurately on category-level word time series, due to richer semantics and less noise. 
(4) Experiment verifies the quality of category-level topics extracted from knowledge base, and the further study on the benchmark \textit{Edinburgh twitter corpus} validates the effectiveness of our proposed transfer learning method for event detection.
\textsc{TransDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。
\keywords{event detection, microblog stream, transfer learning, knowledge base.}
\end{abstract}

\section{Introduction}
Many Web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
Although event detection has been a research topic for a long while\cite{allan1998topic}, event detection in microblog stream is still challenging\cite{atefeh2015survey}.
According to \cite{huang2016probabilistic}, the characteristics of microblog, which are fast changing, high noise, and short length, raise the challenge.

@@

%\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).
%\newpage
\bibliographystyle{unsrt}
\small
\bibliography{paperbib}
